\TitleText

### 2020-10-21 presentation/1_introduction.tex
Rev `.gitignore`, rightly commit all images

\Title {\TitleText}
\Subtitle {Numerical Experiments}
\blank [big]

@@

\Subsubtitle {\DateText}

@@

\I Bound for the Error Norm

@@

\I Conclusion and References
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Background}
{
\I Multiple-input multiple-output (MIMO) communication system has been proposed as part of the 5G specification, but its hardware overhead increases complexity and power consumption.

\I The design of various algorithms requires channel information to be known.

\I Estimation of MIMO channels also results in high complexity, due to the large number of antennae.

\I Meanwhile, millimeter wave (mm-Wave) channels often exhibit sparse properties, which we might exploit to reduce complexity.
}

>>>>

\Title {\TitleText}
\blank [big]

@@

\Subsubtitle {\InstitutionText}

@@

\I Error Analysis

@@

\I Conclusion
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Background}
{
\I Multiple-input multiple-output (MIMO) systems \\ have been suggested in 5G communication.

\I Estimation of MIMO channels results in high complexity, due to a large number of antennae.

\I Meanwhile, millimeter wave (mm-Wave) channels are often sparse due its poor scattering nature

\I According to compressive sensing theory, we might exploit the sparsity to reduce complexity of estimation procedure.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Compressive Sensing}
{
\blank [big]
\externalfigure [compressive-sensing.png] [factor=fit]

\I The signal as shown in is not sparse in the basis on the left, but it is in the basis on the right.

\I Thus, the recovery from just a few components are able to approximate it well.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Work on Compressive Channel Sensing}
{
\I Bajwa, Haupt, Sayeed, and Nowak (2010): MIMO, linear invariant system, using Dantzig Selector (DS)

\I Alkhateeb, Ayach, Leus, Heath (2014): mm-wave channel, adaptive training algorithm for given codebook

\I Alkhateeb, Leus, and Heath (2015): single path mm-wave channel, all-phase-shifter beamformers,
using Orthogonal Matching Pursuit (OMP)

\I Lee, Lee, and Yong (2016): MIMO mm-wave channel, hybrid beamforming, using Orthogonal Matching Pursuit (OMP)
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Our Contribution}
{
\I Consider MIMO mm-wave channel, with hybrid beamforming

\I Use a modified DS (convex programming), instead of OMP (greedy algorithm)

\I Illustrate by experiments that DS has better performance

\I Give an analysis of error norm and successful probability in terms of system parameters
}

### 2020-10-21 presentation/2_setting.tex
Rev `.gitignore`, rightly commit all images

\Frame {Channel Model}
{
\I Consider the uniform linear array
\Disp {
\NC \V {a} \SB {\psi'}
= \NC \F {1}{\R {N_H}} \sum_{n=0}^{N-1} \Ss {e}^{n \psi' \Ss {i}} \V {u}_n
\in \MB {C} ^{N_H} \NR
}

\I Consider the channel representation
\Disp {
\NC \M{H}
=\NC \sum_{l=0} ^{L-1}
\a_l
\V {a} \SB {\f_l'}
\V {a} \SB {\th_l'}^\Adj
\in \MB {C} ^{N_H \D N_H} \NR
}

\I where \m {L} is the number of paths, \m {\f_l'} is related to the angles of arrival, \m {\th_l'} is related to the angles of arrival.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Precoders and Combiners}
{
\I Tx: Digital precoder \m {\M {F}_B \in \NC \MB {C} ^{N_R \D N_Y}}

\I Tx: Analog precoder \m {\NC \M {F}_R \in \NC \MB {C} ^{N_H \D N_R}}

\I Rx: Digital combiner \m {\M {W}_B \in \NC \MB {C} ^{N_R \D N_H}}

\I Rx: Analog combiner \m {\M {W}_R \in \NC \MB {C} ^{N_Y \D N_R}}

\I With the unity magnitude constraint
\Disp {
\NC \Nm {\M {F}_R \SB {n_H, n_R}}
= \NC 1,
\Q \Nm {\M {W}_R \SB {n_R, n_H}}
= 1, \NR
}

\I Under the assumption
\Disp {
\NC N_H \gg \NC N_R \gg N_Y \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Effective Channel}
{
\I Consider Complex Standard Normal \m {\M{Z} \in \NC \MB {C} ^{N_H \D N_H}}

\I Introduce the effective channel
\Disp {
\NC \M{Y}
:=\M{W}_B \M{W}_R \RB {\M{H} \M{F}_R \M{F}_B +\M{Z}} \NR
}

\I Summarizing the dimension,
\Disp {
\NC \MB {C}^{N_Y}
\underset {\M{F}_B} {\mapsto} \NC \MB {C}^{N_R}
\underset {\M{F}_R} {\mapsto} \MB {C}^{N_H}
\underset {\M{H}} {\mapsto} \MB {C}^{N_H}
\underset {\M{W}_R} {\mapsto} \MB {C}^{N_R}
\underset {\M{W}_B} {\mapsto} \MB {C}^{N_Y} \NR
}

\I How do we \Emph {recover} \m {\M {H}} with knowledge of \m {\M {Y}}?

\I How do we \Emph {design} \m {\M {W}_R}, \m {\M {W}_B}, \m {\M {F}_R}, and \m {\M {F}_B}?
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Transform to the Angular Domain}
{
\I Introduce the DFT matrix \m {\M {K} \in \NC \MB {C} ^{N_H \D N_H}}, and write
\Disp {
\NC \V {y}
:= \NC \Rm {vec} \SB {\M {Y}},
\Q \M {P}
:= \RB {\M {F}_B^\Tr \M {F}_R^\Tr \M{K}^\ast} \otimes \RB {\M {W}_B \M {W}_R \M {K}}, \NR
\NC \V {g}
:= \NC \Rm {vec} \SB {\M {K}^\Adj \M {H} \M {K}},
\Q \V {z}
:= \Rm {vec} \SB {\M {Z}} \NR
}

\I Then we have a \Emph {linear equation}
\Disp {
\NC \V {y}
=\NC \M {P} \V {g} +\V {z} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Proposed Method}
{
\I Input \m{\M {P} \in \MB {C} ^{N_Y^2 \D N_H^2}}, \m{\V {y} \in \MB {C} ^{N_H^2}}, \m{\g_{\Ss {DS}} \geq 0}.

@@

\I Output \m {\Hat {\M {H}} \LA \M {K} \Rm {vec}^{-1} \SB {\Hat {g}} \M {K}^\Adj}
}

>>>>

\Frame {Channel Model and Beamformers}
{
\I Given channel \m {\M {H} \in \NC \MB {C} ^{N_H \D N_H}} with uniform linear array

\I Complex standard normal noise \m {\m {Z} \in \NC \MB {C} ^{N_H \D N_H}}

\I Tx: Digital precoder \m {\M {F}_B \in \NC \MB {C} ^{N_R \D N_Y}}
\I Tx: Analog precoder \m {\NC \M {F}_R \in \NC \MB {C} ^{N_H \D N_R}}

\I Rx: Digital combiner \m {\M {W}_B \in \NC \MB {C} ^{N_R \D N_H}}
\I Rx: Analog combiner \m {\M {W}_R \in \NC \MB {C} ^{N_Y \D N_R}}

\I Magnitude constraint \m {\Nm {\M {F}_R \SB {n_H, n_R}} = 1}, \m {\Nm {\M {W}_R \SB {n_R, n_H}} = 1} 
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {System Diagram}
{
\blank [big]
\externalfigure [system.png] [factor=fit]

\I Problem (a): Recover \m {\M {H}} with knowledge of \\
\m {\M {Y} :=\M {W}_B \M {W}_R \RB {\M {H} \M {F}_R \M {F}_B +\M {Z}} }?

\I Problem (b): Design \m {\M {W}_R}, \m {\M {W}_B}, \m {\M {F}_R}, and \m {\M {F}_B}?
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Cast to Linear System}
{
\I Introduce the DFT matrix \m {\M {K} \in \NC \MB {C} ^{N_H \D N_H}}, and write
\Disp {
\NC \V {y}
:= \NC \Rm {vec} \SB {\M {Y}},
\Q \M {P}
:= \RB {\M {F}_B^\Tr \M {F}_R^\Tr \m {K}^\ast} \otimes \RB {\M {W}_B \M {W}_R \M {K}}, \NR
\NC \V {g}
:= \NC \Rm {vec} \SB {\M {K}^\Adj \M {H} \M {K}},
\Q \V {z}
:= \Rm {vec} \SB {\M {Z}} \NR
}

\I Then we have a underdetermined linear system:
\Disp {
\NC \V {y}
=\NC \M {P} \V {g} +\V {z} \NR
}

\I When the signal is sparse, few measurements may be sufficient for the reconstruction
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Terminology}
{
\I \m {\V {g}} is called \Emph {\m {s}-sparse}, if at most \m {s} of its components are nonzero.

\I We say that \m {\M {P}} satisfies the \Emph {restricted isometry property} (RIP) of sparsity \m {s} with respect to \m {0 < \d_s < 1}, if, for all \m {s}-sparse \m {\V {g}},
\Disp {
\NC \RB {1-\d_s} \VNm {\V {g}} _2^2
\leq \NC \VNm {\m {P} \V {g}} _2^2
\leq \RB {1+\d_s} \VNm {\V {g}} _2^2
}

\I We may think \m {\M {P}} to be almost unitary up to relative error \m {\d_s}.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Applying Dantzig Selector}
{
\I We try to apply Dantzig Selector to our problem:

\I Input \m {\M {P} \in \MB {C} ^{N_Y^2 \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_H^2}}, \m {\g_{\Ss {DS}} \geq 0}.

@@

\I Output \m {\Hat {\M {H}} \LA \M {K} \Rm {vec}^{-1} \SB {\Hat {g}} \M {K}^\Adj}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Design of Beamformers}
{
\I Let us set each entry of \m {\m {F}_B} (resp.\ \m {\m {W}_B}) to be i.i.d.\ complex standard normal, up to a design constant

\I And set each entry of \m {\m {F}_R} (resp.\ \m {\m {W}_R}) be uniformly distributed in argument and unity magnitude, up to a design constant

\I We will argue that \m {\M {F} _R ^\Tr}, \m {\M {F} _B ^\Tr}, \m {\M {W} _R}, and \m {\M {W} _B} all have RIP, thus \m {\M {P}} has too.

\I Fix sparsity \m {s = L \RB {\log N_H}^2} for concreteness
}

### 2020-10-21 presentation/3_proof.tex
Rev `.gitignore`, rightly commit all images

\Frame {Modifying the Original Proof (1/2)}
{
\I DS works for real matrices, but we generalize by representing a complex number by its real- and imarinary-parts.

\I DS works for sparse vectors, but \m {\M {H}} is not sparse.
We claim that \m {\M {K}^\Adj \M {H} \M {K}} is almost sparse.
Call the largest-magnitude \m {S} components of \m {\V{g}} to be \m {\M {g} _{\SB{\MC {A}}}}, and call the remaining vector \m {\M {g} _{\SB{\MC {C}}}}, we have to bound \m {\VNm {\M {g} _{\SB{\MC {C}}}} _1}.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Modifying the Original Proof (2/2)}
{
\I DS requires the measurement matrix (in our case) \m {P} to have restricted isometry property.
We shall design all four beamformers, \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}, so that for high probability, they satisfies RIP, thus \m {\m {P}} does too.

\I We know the Big-\m {\MC {O}} of error norm of DS depends on (in our case) \m {N_H}.
We consider these failure events above, and claim that the algorithm works for high probability.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {\m {\V{g}} is Almost Sparse}
{
\I Suppose for concreteness,
\Disp {
\NC S
= L \log N_H,
\Q \d_S
\leq \F {1} {8} \NR
}

\I We may show that 
\Disp {
\NC \VNm {\M {g} _{\SB{\MC {C}}}} _1
\leq \NC \F {4} {3} \RB {\log N_H}^2 \NR
}

\I holds for probability \m {p}, with
\Disp {
\NC 1 -p
\leq \NC 2 \exp \SB {-\F {9L} {\pi}} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Design of Beamformers}
{
\I Let us set each entry of \m {\m {F}_B} (resp.\ \m {\m {W}_B}) to be i.i.d.\ Complex Standard Normal, up to a design constant

\I And set each entry of \m {\m {F}_R} (resp.\ \m {\m {W}_R}) be uniformly distributed argument and unity magnitude, up to a design constant

\I It is argued in the treatise that \m {\M {F} _R ^\Tr}, \m {\M {F} _B ^\Tr}, \m {\M {W} _R}, and \m {\M {W} _B} all have RIP, then \m {\M {P}} has too.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {RIP of Digital Beamformers}
{
\I For \m {0 <\d_s <1}, unit vector \m {\V {u}}, \m {\M {W}_B} (resp.\ \m {\M {F} _B ^\Adj}) satisfies
%
\Disp {
\NC \Nm {\VNm {\M {W} _B \V {u}} _2^2 - 1}
\geq \NC \d_s \NR
}

\I holds for probability \m {p}, with
\Disp {
\NC 1 -p
\leq \NC 2 \Ss {e} ^{-N_Y \R {\d_s} /4} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {RIP of Analog Beamformers}
{
\I Suppose
%
\Disp {
\NC N_R
\geq \NC \F {s} {\d_s^2} \RB {\log s}^2 \log N_H \NR
}
%
\I Then \m {\M {W}_R} (resp.\ \m {\M {F} _R ^\Adj}) has \m {\d_s}-RIP for probability \m {p}, with
\Disp {
\NC 1 -p
\leq \NC \RB {\F {\d_s} {N_H s}} ^{1/3} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Bound of Error Norm (1/2)}
{
\I The following bound holds for probability \m {p}:
\Disp {
\NC \VNm {\Hat {\V {g}} - \V {g}} _2
%
\leq \NC 8 \R {L} \R {\log N_H}^3 \NR
}
%
\I where for \m {p}, denote the four events of failure, subscript respectively for restricted isometry, noise, sparsity,
\Disp {
\NC q = 1-p
\lesssim \NC 2 \RB {q _{\Rm {iso}, B} + q _{\Rm {iso}, R}} +q _{\Rm {no}} +q _{\Rm {sp}} \NR
}

\I Then...
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Bound of Error Norm (2/2)}
{
\I For concreteness, set values
\Disp {
\NC N_Y \gtrsim \NC 4 \log N_H, \NR
\NC N_R \gtrsim \NC 16 L \RB {\log N_H}^2 \NR
}
%
\I It follows that
\Disp {
\NC q _{\Rm {sp}}
\lesssim \NC q _{\Rm {no}}
\lesssim q _{\Rm {iso}, B}
\eqsim q _{\Rm {iso}, R} \NR
%
\NC q
\lesssim \NC 2 N_H ^{-1/3} \NR
}
}

>>>>

\Frame {Error Analysis}
{
\I What's the difference of true value \m {\V {h}} and estimated value \m {\Hat {\V {h}}}?

\I Should account for the fact that \m {\V {g}} is not strictly sparse

\I Should justify that all four beamformers, \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}, have RIP for high probability, thus \m {\m {P}} does too.

\I Should investigate the Big \m {\MC {O}} of error norm by bounding failure events mentioned above.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {The Bound}
{
\I In conclusion, it holds for probability \m {p} that
\Disp {
\NC \VNm {\Hat {\V {g}} - \V {g}} _2
%
\leq \NC 8 \R {L} \RB {\log N_H} ^{3/2} \NR
}
%
\I For design values
\Disp {
\NC N_Y \gtrsim \NC 4 \log N_H, \Q
N_R \gtrsim 16 L \RB {\log N_H}^2 \NR
}
%
\I And it holds that
\Disp {
\NC 1 - p
\lesssim \NC 2 N_H ^{-1/3} \NR
}
%
\I Unfortunately, the values are too big to simulate.
}

### 2020-10-21 presentation/4_simulation.tex
Rev `.gitignore`, rightly commit all images

% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Linear Programming}
{
\I Set \m {\V {1} = \IP {1, \dots, 1}}.
\I Calculate
\Disp {
\NC \Hat {\V {g}}, \Hat {\V {f}}
\LA \NC \startcases
   \NC \Min {\V {g}', \V {f}'}  \MC \IP {\V {1}, \V {f}'} \NR
   \NC \Rm {subject} \; \Rm {to} \MC \V {g}' \leq \V {f}' \NR
   \NC \MC - \V {g}' \leq \V {f}' \NR
   \NC \MC \M {P}^\Adj \M {P} \V {g}' \leq \M {P}^\Adj \V {y} + \g_{\Ss {DS}} \V {1} \NR
   \NC \MC - \M {P}^\Adj \M {P} \V {g}' \leq - \M {P}^\Adj \V {y} + \g_{\Ss {DS}} \V {1} \NR
\stopcases \NR
}
\I Output \m {\Hat {\M {H}} \LA \M {K} \Rm {vec}^{-1} \SB {\Hat {g}} \M {K}^\Adj}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Two-Stage Estimation (1/2)}
{
\I Denote
\Disp {
\NC N_0 = \NC 2 N_H^2 \NR
\NC N_1 = \NC 2 N_H \NR
\NC N_2 = \NC 2 \lfloor \Rm {min} \SB {L \log \SB {N_H^2}, N_H} \rfloor \NR
}

\I Apply DS to \m {\V {y}, \M {P}} to get \m {\Hat {\V {g}}_0}.

\I Choose the \m {N_1} largest component of \m {\Hat {\V {g}}_0} and call it \m {\V {g}_1}.
Choose corresponding columns of \m {\M {P}} and call it \m {\M {P} _1}.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Two-Stage Estimation (2/2)}
{
\I Apply DS to \m {\V {y}, \M {P} _1} to get \m {\Hat {\V {g}}_1}.

\I Choose the \m {N_2} largest component of \m {\Hat {\V {g}}_1} and call it \m {\V {g}_2}.
Choose corresponding columns of \m {\M {P}_1} and call it \m {\M {P} _2}.

\I Apply pseudoinverse (linear square) to \m {\V {y}, \M {P} _2} to get \m {\Hat {\V {g}}_2}.

\I Assign corresponding components of \m {\Hat {\V {g}}_2} in \m {\Hat {\V {g}}}, and pad \m {0} otherwise.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Performance Metric}
{
\I With some approximations, I suggest the following metric for spectral efficiency:
\I Denote \m {E := \Hat {H} - H}
\I Observe
\Disp {
\NC \VNm {\RB {\M {H} + \M {E}} \RB {\M {H} + \M {E}} ^\Adj - \M {H} \M {H} ^\Adj} \V {x}
\lesssim 2 \VNm {\M {E}} _2 \VNm {\M {H}} _2 \VNm {\V {x}} \NR
}
\I Define the spectral efficiency to be
\Disp {
\NC \log \det \SB {I + \RB {\s + \F {2 \VNm {\M {E}} _2 \VNm {\M {H}} _2} {N_H ^{3/2}}} ^{-1} \M {H} \M {H} ^ \Adj} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Theoretical Metric}
{
\I For the theoretical error norm,
\Disp {
\NC \log d_{\Rm {th}}
\lesssim \NC \F {1} {2} \log L +\F {3} {2} \log \log N_H \NR
}
\I Define the theoretical spectral efficiency to be
\Disp {
\NC \log \det \SB {I + \RB {\s + \F {2 d_{\Rm {th}} \VNm {\M {H}} _2} {N_H ^{3/2}}} ^{-1} \M {H} \M {H} ^ \Adj} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Simulation Parameters}
{
\I Antennae number of channel \m {N_H = 16, 20, 24}
\I Antennae number of analog stage \m {N_R = \lfloor \R {N_H N_Y} \rfloor}
\I Antennae number of digital stage \m {N_Y = \lfloor N_H/3 \rfloor}
\I Number of paths \m {L =3}
\I Analog beamformer quantization grid: \m {16}
\I How many noise standard deviation tried: \m {7}
\I Number of repetition of each data point: \m {12}
\I Solved by Python CVXPY
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Spectral Efficiency, \m {N_H=16}}
{
\blank [big]
\externalfigure [assorted-small-efficiency.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Time Taken, \m {N_H=16}}
{
\blank [big]
\externalfigure [assorted-small-time.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Spectral Efficiency, \m {N_H=20}}
{
\blank [big]
\externalfigure [assorted-medium-efficiency.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Time Taken, \m {N_H=20}}
{
\blank [big]
\externalfigure [assorted-medium-time.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Spectral Efficiency, \m {N_H=24}}
{
\blank [big]
\externalfigure [assorted-big-efficiency.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Time Taken, \m {N_H=24}}
{
\blank [big]
\externalfigure [assorted-big-time.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Discussion}
{
\I DS is slightly better than others when \m {\s \gg 1}

\I \m {\eta _{\Ss {th}}} is in correct order of magnitude but not tight when \m {\s \gg 1}

\I The smaller the noise, the smaller the error

\I It is \It {not} true that the smaller \m {\g _{\Ss {DS}}}, the smaller the error

\I We have exceedingly high complexity than OMP

\I The requirement that \m {N_H \gg N_Y} is demanding
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Complexity (1/2)}
{
\I In general, the complexity of convex optimization is hard to obtain.

\I However, there exist expressions for number of Newton steps in the course of optimization.
It is \m {\MC {O} \SB {\VNm {\V {g} _0 - \V {g} ^\star} _1}}, where \m {\VNm {\V {g} _0} _1} is the starting value, \m {\V {g} ^\star} the true value.
Assume that is \m {\MC {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _1}}, which is at most \m {\MC {O} \SB {N_H^2}}.

\I Moreover, every Newton step requires a matrix inversion of dimension \m {N_H^2}, with at least \m {\MC {O} \SB {N_H^4}}.
This gives \m {\MC {O} \SB {N_H^6}}.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Complexity (2/2)}
{
\I On the other hand, it is pointed out that Lasso (least absolute shrinkage and selection operator) has similar complexity with Least Angle regression, which has complexity \m {\MC {O} \SB {N_H^6}}.
Since DS and Lasso have similar form, we expect DS has similar complexity.

\I Clearly, the complexity of OMP is at most \m {\MC {O} \SB {N_H^2}}, so much smaller than DS.
}

>>>>

% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Linear Programming}
{
\I DS is equivalent to a linear program, which allows more efficient convex programming methods to be used.

\I Calculate
\Disp {
\NC \Hat {\V {g}}, \Hat {\V {f}}
\LA \NC \startcases
   \NC \Min {\V {g}', \V {f}'}  \MC \IP {\V {1}, \V {f}'} \NR
   \NC \Rm {subject} \; \Rm {to} \MC \V {g}' \leq \V {f}' \NR
   \NC \MC - \V {g}' \leq \V {f}' \NR
   \NC \MC \M {P}^\Adj \M {P} \V {g}' \leq \M {P}^\Adj \V {y} + \g_{\Ss {DS}} \V {1} \NR
   \NC \MC - \M {P}^\Adj \M {P} \V {g}' \leq - \M {P}^\Adj \V {y} + \g_{\Ss {DS}} \V {1} \NR
\stopcases \NR
}
\I Output \m {\Hat {\M {H}} \LA \M {K} \Rm {vec}^{-1} \SB {\Hat {g}} \M {K}^\Adj}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Two-Stage Estimation}
{
\I Candès and Tao suggests a two stage version may be used to improve precision.

\I Choose \m {N_0 = 2 N_H^2, N_2 = \lfloor 4 \log N_H \rfloor, N_1 = \lfloor \R {N_0 N_2} \rfloor}

\I Apply DS to \m {\V {y}, \M {P}} to get \m {\Hat {\V {g}}_0}, and take the \m {N_1} largest component of \m {\Hat {\V {g}}_0} to be \m {\V {g}_1}, and corresponding columns of \m {\M {P}} to be \m {\M {P} _1}.

\I Apply DS to \m {\V {y}, \M {P}_1} to get \m {\Hat {\V {g}}_1}, and take the \m {N_2} largest component of \m {\Hat {\V {g}}_1} and to be \m {\V {g}_2}, and corresponding columns of \m {\M {P}} to be \m {\M {P} _2}.

\I Apply least square to \m {\V {y}, \M {P} _2} to get \m {\Hat {\V {g}}_2}, which corresponds to \m {\Hat {\V {g}}}.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Performance Metric}
{
\I We call the following quantity \m {\chi} efficiency, which is suggestive of the MIMO channel capacity.

\I Denote \m {\M {E} = \Hat {\M {H}} - \M {H}}.
\Disp {
\NC \chi
= \log \det \SB {\M {I} + \RB {\s + \F {2 \VNm {\M {E}} _2 \VNm {\M {H}} _2} {N_H ^{3/2}}} ^{-1} \M {H} \M {H} ^ \Adj} \NR
}

\I The theoretical efficiency \m {\chi _{\Rm {th}}} is defined by plugging in \m {\V {d}}.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Efficiency, \m {N_H=8}}
{
\blank [big]
\externalfigure [assorted-very-small-spectral.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Efficiency, \m {N_H=12}}
{
\blank [big]
\externalfigure [assorted-small-spectral.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Efficiency, \m {N_H=16}}
{
\blank [big]
\externalfigure [assorted-medium-spectral.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Efficiency, \m {N_H=20}}
{
\blank [big]
\externalfigure [assorted-big-spectral.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Efficiency, \m {N_H=24}}
{
\blank [big]
\externalfigure [assorted-very-big-spectral.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Time, \m {N_H=16}}
{
\blank [big]
\externalfigure [assorted-medium-time.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Discussion}
{
\I DS wins narrowly for smaller \m {\s}, but deteriorates for larger \m {\s}.

\I \m {\chi _{\Ss {th}}} is accurate for larger \m {\s}, but overestimates for smaller \m {\s}.

\I The weaker constraint on sparsity conpromises DS's performance.

\I DS has complexity much higher than OMP, but similar to Lasso.

\I As \m {2N_H^2} grows fast, DS becomes less feasible.

\I The two-stage version is not always better.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {A Successful Case of Estimation}
{
\blank [big]
\externalfigure [scatter-ddss-success.png] [wfactor=150]

\I When DS succeeds: soft thresholding (green) correctly guesses the true values of non-zero positions (black), and refines the estimated value (orange)
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {A Failed Case of Estimation}
{
\blank [big]
\externalfigure [scatter-ddss-failure.png] [wfactor=150]

\I When DS fails: soft thresholding (green) does not correctly guess the true values of non-zero positions (black), and the estimated value (orange) becomes worse
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Complexity}
{
\I The number of Newton steps is about \m {\MC {O} \SB {\VNm {\V {g} _0 - \V {g} ^\star} _1}}, where \m {\VNm {\V {g} _0} _1} is the starting value, \m {\V {g} ^\star} the true value.
Assume that is \m {\MC {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _1}}, or \m {\MC {O} \SB {N_H^2}}.

\I Every Newton step requires a matrix inversion of dimension \m {2 N_H^2}, with complexity \m {\MC {O} \SB {N_H^4}}, giving overall complexity \m {\MC {O} \SB {N_H^6}}.

\I Complexity of Lasso can be similarly argued to be \m {\MC {O} \SB {N_H^6}}.

\I Clearly, OMP has complexity \m {\MC {O} \SB {N_H^2}}, much smaller than DS.
}
